Effect of quality-adjusted production function inputs

### 2015-05-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now contains graphs.

>>>>

\begin{table} \caption{Unadjusted time-series variables.} 
\label{tab:unadjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal           & UK                 \\
      \midrule
      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{Quality-adjusted time series variables.} 
\label{tab:quality_adjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal         & UK               \\
      \midrule
      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

Unadjusted and quality-adjusted data for both Portugal and the United Kingdom 
are shown in Figure~\ref{fig:Historical Data}.

<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Historical data.", warning=FALSE>>=
unadjVars_PT <- c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj)
unadjVars_UK <- c(y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj)
commonVars <- c("Year", "iYear", "Country")
unadjData_PT <- historicalData[ , as.character(unique(c(unadjVars_PT, commonVars)))] %>% filter(Country=="PT")
unadjData_UK <- historicalData[ , as.character(unique(c(unadjVars_UK, commonVars)))] %>% filter(Country=="UK")
unadjData <- plyr::rbind.fill(unadjData_PT, unadjData_UK)
unadjData$adjusted <- "Unadjusted"

adjVars_PT <- c(y_PT, k_PT_adj, l_PT_adj, e_PT_adj)
adjVars_UK <- c(y_UK, k_UK_adj, l_UK_adj, e_UK_adj)
adjData_PT <- historicalData[ , as.character(unique(c(adjVars_PT, commonVars)))] %>% filter(Country=="PT")
adjData_UK <- historicalData[ , as.character(unique(c(adjVars_UK, commonVars)))] %>% filter(Country=="UK")
adjData <- plyr::rbind.fill(adjData_PT, adjData_UK)
adjData$adjusted <- "Quality-adjusted"

trimmedData <- plyr::rbind.fill(unadjData, adjData)

mdata <- melt(trimmedData, 
              measure.vars = unique(as.character(c(unadjVars_PT, unadjVars_UK, adjVars_PT, adjVars_UK))), 
              variable.name = "variable",
              value.name = "value")

# Relevel factors before plotting
mdata$Country <- relevelFactor(as.factor(mdata$Country), c("PT", "UK"))
mdata$adjusted <- relevelFactor(as.factor(mdata$adjusted), c("Unadjusted", "Quality-adjusted"))
mdata$variable <- relevelFactor(as.factor(mdata$variable), unique(as.character(
  c(y_PT, k_PT_unadj, l_PT_unadj, e_PT_unadj, k_PT_adj, l_PT_adj, e_PT_adj,
    y_UK, k_UK_unadj, l_UK_unadj, e_UK_unadj, k_UK_adj, l_UK_adj, e_UK_adj))))

historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ adjusted, 
               line_types = c(1,2,4,3,2,4,3,2,3,2,3)) + 
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
  coord_cartesian(ylim=c(0.5, 13)) +
  xlab("") + 
  ylab("Indexed (1960=1)")
@
